---
title: "HCAMP Baseline and Post-Injury Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(rio)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(glue)
library(fs)
library(rstatix)
library(ggpubr)


theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )


files <- dir_ls(here::here("data"), glob = "*.csv")

d <- map_df(files, read_csv, .id = "file",
                 col_types = cols(.default = "c")) %>% 
  modify(~parse_guess(.x)) %>% 
  janitor::clean_names() %>% 
  mutate(year = parse_number(file)) %>% 
  mutate(year = as.factor(year))

mean_2 <- function(x) {
  z <- na.omit(x)
  sum(z) / length(z)
}

str(d)
d$user_symptom22delayed
d$user_symptom11delayed

impact2 <- d %>% 
  mutate(user_gender = as.factor(user_gender),
         user_age = as.factor(user_age),
         org_name = as.factor(org_name),
         user_handedness = as.factor(user_handedness),
         user_height = as.factor(user_height),
         user_weight = as.factor(user_weight),
         user_country = as.factor(user_country),
         user_first_language = as.factor(user_first_language),
         user_second_language = as.factor(user_second_language),
         user_education_level = as.factor(user_education_level),
         user_special_ed1 = as.factor(user_special_ed1),
         user_special_ed2 = as.factor(user_special_ed2),
         user_special_ed3 = as.factor(user_special_ed3),
         user_special_ed4 = as.factor(user_special_ed4),
         user_special_ed5 = as.factor(user_special_ed5),
         add_adhd = as.factor(add_adhd),
         dyslexia = as.factor(dyslexia),
         autism = as.factor(autism),
         user_treatment_received1 = as.factor(user_treatment_received1),
         user_treatment_received2 = as.factor(user_treatment_received2),
         user_treatment_received3 = as.factor(user_treatment_received3),
         user_treatment_received4 = as.factor(user_treatment_received4),
         user_treatment_received5 = as.factor(user_treatment_received5),
         user_treatment_received6 = as.factor(user_treatment_received6),
         user_treatment_received7 = as.factor(user_treatment_received7),
         user_current_sport = as.factor(user_current_sport),
         user_primary_position = as.factor(user_primary_position),
         user_level_of_participation = as.factor(user_level_of_participation),
         user_years_playing = as.factor(user_years_playing),
         user_number_of_concussions = as.factor(user_number_of_concussions),
         user_concussion_type1 = as.factor(user_concussion_type1),
         user_concussion_type2 = as.factor(user_concussion_type2),
         user_concussion_type3 = as.factor(user_concussion_type3),
         user_concussion_type4 = as.factor(user_concussion_type4),
         user_total_games_missed = as.factor(user_total_games_missed),
         user_concussion_history = as.factor(user_concussion_history),
         user_last_concussion_date = as.factor(user_last_concussion_date),
         test_type = as.factor(test_type),
         test_date = as.factor(test_date),
         exam_language = as.factor(exam_language),
         test_version = as.factor(test_version),
         word_memory_lp = as.factor(word_memory_lp),
         word_memory_dm_correct = as.factor(word_memory_dm_correct),
         word_memory_total_percent_correct = as.factor(word_memory_total_percent_correct),
         design_memory_lp = as.factor(design_memory_lp),
         design_memory_dm_correct = as.factor(design_memory_dm_correct),
         design_memory_total_percent_correct = as.factor(design_memory_total_percent_correct),
         x_oaverage_incorrect = as.factor(x_oaverage_incorrect),
         three_letters_percentage_letters_correct = as.factor(three_letters_percentage_letters_correct),
         user_symptom1delayed = as.factor(user_symptom1delayed))

str(impact2)

impact2$user_symptom1delayed


impact3 <- impact2 %>% 
  mutate(user_age = as.numeric(user_age),
         user_height = as.numeric(user_height),
         user_weight = as.numeric(user_weight),
         user_education_level = as.numeric(user_education_level),
         user_years_playing = as.numeric(user_years_playing),
         user_number_of_concussions = as.numeric(user_number_of_concussions),
         user_concussion_type1 = as.numeric(user_concussion_type1),
         user_concussion_type2 = as.numeric(user_concussion_type2),
         user_concussion_type3 = as.numeric(user_concussion_type3),
         user_concussion_type4 = as.numeric(user_concussion_type4),
         user_total_games_missed = as.numeric(user_total_games_missed),
         word_memory_lp = as.numeric(word_memory_lp),
         word_memory_dm_correct = as.numeric(word_memory_dm_correct),
         word_memory_total_percent_correct = as.numeric(word_memory_total_percent_correct),
         design_memory_lp = as.numeric(design_memory_lp),
         design_memory_dm_correct = as.numeric(design_memory_dm_correct),
         design_memory_total_percent_correct = as.numeric(design_memory_total_percent_correct),
         x_oaverage_incorrect = as.numeric(x_oaverage_incorrect),
         three_letters_percentage_letters_correct = as.numeric(three_letters_percentage_letters_correct),
         user_symptom1delayed = as.numeric(user_symptom1delayed))

str(impact3)

mean_2(impact3$user_symptom1delayed)
mean_2(impact3$user_symptom2delayed)
mean_2(impact3$user_age)

impact <- impact3

str(impact)

impact$user_current_sport
```

```{r code needed for rest of document, include=FALSE}

test_time_baseline <- impact %>% 
  dplyr::select(year,
         passport_id, 
         user_gender, 
         user_age, 
         org_name,
         test_type, 
         test_date, 
         test_version, 
         user_current_sport,
         user_number_of_concussions,
         user_education_level,
         user_memory_composite_score_verbal,
         user_memory_composite_score_visual,
         user_impulse_control_composite_score,
         user_visual_motor_composite_score,
         user_reaction_time_composite_score,
         user_impulse_control_composite_score) 

str(test_time_baseline)

test_time_baseline <- test_time_baseline %>% 
  filter(test_type != "Baseline ++")

test_time_baseline <- test_time_baseline %>% 
  filter(test_type != "Post-Injury 2")

test_time_baseline <- test_time_baseline %>% 
  filter(test_type != "Post-Injury 3")

test_time_baseline <- test_time_baseline %>% 
  filter(test_type != "Post-Injury 4")


test_time_baseline %>% 
  arrange(passport_id)

baseline <- test_time_baseline %>% 
  filter(test_type == "Baseline") 

str(baseline)

baseline3 <- baseline %>% 
  group_by(passport_id) %>% 
  filter(n() > 1) %>% 
  mutate(baseline_number = row_number()) %>% 
  spread(baseline_number, test_type, sep = "_") %>% 
  arrange(passport_id)


baseline3 <- baseline3[, -c(18:24)]

str(baseline3)

baseline3 %>% 
  count(passport_id)


head(baseline3)

baseline3$test_date <- as.Date(baseline3$test_date, format = "%m/%d/%Y")

mem_verbal <- baseline3 %>% 
  group_by(passport_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = passport_id,
    names_from = number,
    values_from = c(test_date, user_memory_composite_score_verbal),
    names_glue = "{.value}_{number}"
  ) 

mem_verbal <- mem_verbal %>% 
  dplyr::select(passport_id, 
         test_date_1, 
         test_date_2, 
         user_memory_composite_score_verbal_1, 
         user_memory_composite_score_verbal_2) %>% 
  mutate(memory_verbal_diff = user_memory_composite_score_verbal_2 - user_memory_composite_score_verbal_1)

mem_verbal_all <- mem_verbal

mem_verbal <- mem_verbal %>% 
  filter(memory_verbal_diff > 0)

mem_verbal <- mem_verbal %>% 
  mutate(memory_verbal_percent_inc = memory_verbal_diff / user_memory_composite_score_verbal_1 * 100)

mean_2(mem_verbal$memory_verbal_diff)
mean_2(mem_verbal$memory_verbal_percent_inc)

mem_visual <- baseline3 %>% 
  group_by(passport_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = passport_id,
    names_from = number,
    values_from = c(test_date, user_memory_composite_score_visual),
    names_glue = "{.value}_{number}"
  ) 

mem_visual <- mem_visual %>% 
  dplyr::select(passport_id, 
         test_date_1, 
         test_date_2, 
         user_memory_composite_score_visual_1, 
         user_memory_composite_score_visual_2) %>% 
  mutate(memory_visual_diff = user_memory_composite_score_visual_2 - user_memory_composite_score_visual_1)

mem_visual_all <- mem_visual

mem_visual <- mem_visual %>% 
  filter(memory_visual_diff > 0)

mean_2(mem_visual$memory_visual_diff)

mem_visual <- mem_visual %>% 
  mutate(memory_visual_percent_inc = memory_visual_diff / user_memory_composite_score_visual_1 * 100)

visual_motor <- baseline3 %>% 
  group_by(passport_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = passport_id,
    names_from = number,
    values_from = c(test_date, user_visual_motor_composite_score),
    names_glue = "{.value}_{number}"
  ) 

visual_motor <- visual_motor %>% 
  dplyr::select(passport_id, 
         test_date_1, 
         test_date_2, 
         user_visual_motor_composite_score_1, 
         user_visual_motor_composite_score_2) %>% 
  mutate(visual_motor_diff = user_visual_motor_composite_score_2 - user_visual_motor_composite_score_1)

visual_motor_all <- visual_motor

visual_motor <- visual_motor %>% 
  filter(visual_motor_diff > 0)

visual_motor <- visual_motor %>% 
  mutate(visual_motor_percent_inc = visual_motor_diff / user_visual_motor_composite_score_1 * 100)


impulse_control <- baseline3 %>% 
  group_by(passport_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = passport_id,
    names_from = number,
    values_from = c(test_date, user_impulse_control_composite_score),
    names_glue = "{.value}_{number}"
  ) 

impulse_control <- impulse_control %>% 
  dplyr::select(passport_id, 
         test_date_1, 
         test_date_2, 
         user_impulse_control_composite_score_1, 
         user_impulse_control_composite_score_2) %>% 
  mutate(impulse_control_diff = user_impulse_control_composite_score_1 - user_impulse_control_composite_score_2)

impulse_control_all <- impulse_control

impulse_control <- impulse_control %>% 
  filter(impulse_control_diff > 0)

impulse_control <- impulse_control %>% 
  mutate(impulse_control_percent_dec = impulse_control_diff / user_impulse_control_composite_score_1 * 100)

reaction_time <- baseline3 %>% 
  group_by(passport_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = passport_id,
    names_from = number,
    values_from = c(test_date, user_reaction_time_composite_score),
    names_glue = "{.value}_{number}"
  ) 

reaction_time <- reaction_time %>% 
  dplyr::select(passport_id, 
         test_date_1, 
         test_date_2, 
         user_reaction_time_composite_score_1, 
         user_reaction_time_composite_score_2) %>% 
  mutate(reaction_time_diff = user_reaction_time_composite_score_1 - user_reaction_time_composite_score_2)

reaction_time_all <- reaction_time

reaction_time <- reaction_time %>% 
  filter(reaction_time_diff > 0)

reaction_time <- reaction_time %>% 
  mutate(reaction_time_percent_dec = reaction_time_diff / user_reaction_time_composite_score_1 * 100)


mem_verbal <- mem_verbal %>% 
  arrange(passport_id) %>% 
  na.omit()

mem_verbal_all <- mem_verbal_all %>% 
  na.omit()

mem_visual <- mem_visual %>% 
  arrange(passport_id) %>% 
  na.omit()

mem_visual_all <- mem_visual_all %>% 
  na.omit()

impulse_control <- impulse_control %>% 
  arrange(passport_id) %>% 
  na.omit()

impulse_control_all <- impulse_control_all %>% 
  na.omit()

reaction_time <- reaction_time %>% 
  arrange(passport_id) %>% 
  na.omit()

reaction_time_all <- reaction_time_all %>% 
  na.omit()

visual_motor <- visual_motor %>% 
  arrange(passport_id) %>% 
  na.omit()

visual_motor_all <- visual_motor_all %>% 
  na.omit()

test_join <- full_join(mem_verbal, mem_visual)

test_join2 <- full_join(test_join, impulse_control)

test_join3 <- full_join(test_join2, reaction_time)

baseline_final <- full_join(test_join3, visual_motor)
head(baseline_final)

mean_2(impulse_control$impulse_control_diff)
mean_2(baseline_final$impulse_control_diff)


baseline_all_positive <- baseline_final %>% 
  na.omit()

all_join1 <- full_join(mem_verbal_all, mem_visual_all)

all_join2 <- full_join(all_join1, impulse_control_all)

all_join3 <- full_join(all_join2, reaction_time_all)

all_double_baseline <- full_join(all_join3, visual_motor_all)



create_react <- function(df, var) {
    df %>% 
      summarize(Mean = mean({{var}}),
                SD = sd({{var}}),
                Min = min({{var}}),
                Max = max({{var}}),
                Total = length({{var}})) %>% 
      mutate_if(is.numeric, round, 2) %>% 
      reactable(columns = list(
        Mean = colDef(format = colFormat(separators = TRUE)),
        SD = colDef(format = colFormat(separators = TRUE)),
        Min = colDef(format = colFormat(separators = TRUE)),
        Max = colDef(format = colFormat(separators = TRUE)),
        Total = colDef(format = colFormat(separators = TRUE, suffix = " individuals"))
      ))
}

react_percent <- function(df, var) {
  df %>% 
    summarize(Mean = mean({{var}}),
              SD = sd({{var}}),
              Min = min({{var}}),
              Max = max({{var}}),
              Total = length({{var}})) %>% 
    mutate_if(is.numeric, round, 2) %>% 
    reactable(columns = list(
      Mean = colDef(format = colFormat(separators = TRUE, suffix = "%")),
      SD = colDef(format = colFormat(separators = TRUE, suffix = "%")),
      Min = colDef(format = colFormat(separators = TRUE, suffix = "%")),
      Max = colDef(format = colFormat(separators = TRUE, suffix = "%")),
      Total = colDef(format = colFormat(separators = TRUE, suffix = " individuals"))
      ))
}

baseline_tbl1 <- baseline_all_positive 

head(baseline_final)

```

```{r, extract descriptor variables, include=FALSE}
#age 

age <- baseline3 %>% 
  group_by(passport_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = passport_id,
    names_from = number,
    values_from = c(test_date, user_age),
    names_glue = "{.value}_{number}"
  ) 

age <- age %>% 
  dplyr::select(passport_id,
         test_date_1,
         test_date_2,
         user_age_1,
         user_age_2)

str(age)

# school 

school <- baseline3 %>% 
  group_by(passport_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = passport_id,
    names_from = number,
    values_from = c(test_date, org_name),
    names_glue = "{.value}_{number}"
  ) 

school <- school %>% 
  dplyr::select(passport_id,
         test_date_1,
         test_date_2,
         org_name_1,
         org_name_2)

# sport

sport <- baseline3 %>% 
  group_by(passport_id) %>% 
  mutate(number = row_number()) %>% 
  ungroup() %>% 
  pivot_wider(
    id_cols = passport_id,
    names_from = number,
    values_from = c(test_date, user_current_sport),
    names_glue = "{.value}_{number}"
  ) 

sport <- sport %>% 
  dplyr::select(passport_id,
         test_date_1,
         test_date_2,
         user_current_sport_1,
         user_current_sport_2)
```

```{r join baseline variables, include=FALSE}
blj_1 <- full_join(age, school)
blj_2 <- full_join(blj_1, sport)

baseline_final <- left_join(baseline_final, blj_2)

baseline_all_positive <- left_join(baseline_all_positive, blj_2)

all_double_baseline <- left_join(all_double_baseline, blj_2)

```

```{r baseline numbers, include=FALSE}
total_two_baselines <- all_double_baseline %>% 
  summarize(length(passport_id))

total_one_positive <- baseline_final %>% 
  summarize(length(passport_id))

total_all_positive <- baseline_all_positive %>% 
  summarize(length(passport_id))

t_sum <- data.frame("Level" = c("Two Baseline Assessments", "Gain on at least one Baseline 2 Composite Score", "Gain on all Baseline 2 Composite Scores"), "Total" = c(18739, 18395, 1653))


score_hist <- function(df, x) {
  ggplot(df, aes({{x}})) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
    labs(x = "Test Score",
         y = "Number of Individuals")
}
```

# Background Information {.tabset .tabset-fade .tabset-pills}

## Sample Size 

```{r baseline numbers table, include=TRUE}
t_sum %>% 
  reactable(columns = list(
    Level = colDef(name = "Level"),
    Total = colDef(name = "Total", 
                   format = colFormat(separators = TRUE, suffix = " individuals"))),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE)
```

## Age Range Baseline 1

```{r, include=TRUE}
create_react(all_double_baseline, user_age_1)
```

## Age Totals Baseline 1

```{r, include=FALSE}
age_tbl_1 <- all_double_baseline %>% 
  group_by(user_age_1) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      user_age_1 = colDef(name = "Age"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

age_tbl_1
```

```{r, include=TRUE}
age_tbl_1
```

## Age Range Baseline 2

```{r, include=TRUE}
create_react(all_double_baseline, user_age_2)
```

## Age Totals Baseline 2

```{r, include=FALSE}
age_tbl_2 <- all_double_baseline %>% 
  group_by(user_age_2) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      user_age_2 = colDef(name = "Age"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

age_tbl_2
```

```{r, include=TRUE}
age_tbl_2
```

## School Baseline 1

```{r, include=FALSE}

school_tbl_1 <- all_double_baseline %>% 
  group_by(org_name_1) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      org_name_1 = colDef(name = "School"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

school_tbl_1
```

```{r, include=TRUE}
school_tbl_1
```

## School Baseline 2

```{r, include=FALSE}

school_tbl_2 <- all_double_baseline %>% 
  group_by(org_name_2) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      org_name_2 = colDef(name = "School"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

school_tbl_2
```

```{r, include=TRUE}
school_tbl_2
```


## Sport Baseline 1

```{r, include=FALSE}

sport_tbl_1 <- all_double_baseline %>% 
  group_by(user_current_sport_1) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      user_current_sport_1 = colDef(name = "Sport"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

sport_tbl_1
```

```{r, include=TRUE}
sport_tbl_1
```

## Sport Baseline 2

```{r, include=FALSE}

sport_tbl_2 <- all_double_baseline %>% 
  group_by(user_current_sport_2) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      user_current_sport_2 = colDef(name = "Sport"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

sport_tbl_2
```

```{r, include=TRUE}
sport_tbl_2
```

# Baseline Percent Increase from Test 1 to Test 2 

## Verbal Memory - Baseline 2 Increase Only {.tabset .tabset-fade .tabset-pills}

10,441 individuals (55.72%) increased their verbal memory composite score on the second baseline test administration. 

### Baseline 1 Summary 

The average Baseline 1 score was observed to be 79 points with a standard deviation of 9.32. The minimum score was observed to be 42, and the maximum score was observed to be 99.

```{r, include=TRUE}
create_react(mem_verbal, user_memory_composite_score_verbal_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(mem_verbal, user_memory_composite_score_verbal_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 88.76 points with a standard deviation of 8.12. The minimum score was observed to be 54, and the maximum score was observed to be 100.

```{r, include=TRUE}
create_react(mem_verbal, user_memory_composite_score_verbal_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(mem_verbal, user_memory_composite_score_verbal_2)
```


### Score Increase Summary

The average point increase from baseline 1 to baseline 2 was observed to be 9.76 points with a standard deviation of 6.94 points. The mininum point increase was observed to be 1, while the maximum point increase was observed to be 44. 

```{r verbal memory table 1, include=TRUE}
create_react(mem_verbal, memory_verbal_diff)
```

### Score Increase Histogram 

```{r histogram gain development, include=FALSE}

ggplot(mem_verbal, aes(memory_verbal_diff)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  labs(x = "Point Increase on Baseline 2",
       y = "Number of Individuals")

score_diff_hist <- function(df, x) {
  ggplot(df, aes({{x}})) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
    labs(x = "Point Increase on Baseline 2",
         y = "Number of Individuals")
}


score_diff_hist(mem_verbal, memory_verbal_diff)

percent_inc_hist <- function(df, x) {
  ggplot(df, aes({{x}})) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 100) +
  scale_x_continuous("Percent Increase on Baseline 2", labels = function(x) paste0(x, "%")) +
    labs(x = "Percent Increase on Baseline 2",
         y = "Number of Individuals")
}

percent_inc_hist(mem_verbal, memory_verbal_percent_inc) #not too helpful - maybe density plot

percent_inc_density <- function(df, x) {
  ggplot(df, aes({{x}})) +
  geom_density(fill = "#56B4E9",
               bw = 15) +
  scale_x_continuous("Percent Increase on Baseline 2", labels = function(x) paste0(x, "%")) +
    labs(x = "Percent Increase on Baseline 2",
         y = "Density")
}

percent_inc_density(mem_verbal, memory_verbal_percent_inc)
```

```{r}
score_diff_hist(mem_verbal, memory_verbal_diff)
```

### Percent Increase Summary

The average percent increase from baseline 1 to baseline 2 was observed to be a 13.14% increase with a standard deviation of a 10.71% increase.  

```{r verbal memory table 2, include=TRUE}
react_percent(mem_verbal, memory_verbal_percent_inc)
```

### Percent Increase Density Plot
```{r, include=TRUE}
percent_inc_density(mem_verbal, memory_verbal_percent_inc)
```

## Verbal Memory - Increase on all Five Scores {.tabset .tabset-fade .tabset-pills}

This section summarizes the verbal memory composite score for the 1,653 individuals who achieved a higher score on all five composite scores of the second baseline test administration.  

### Baseline 1 Summary 

The average Baseline 1 score was observed to be 78.19 points with a standard deviation of 9.59. The minimum score was observed to be 43, and the maximum score was observed to be 99.

```{r, include=TRUE}
create_react(baseline_all_positive, user_memory_composite_score_verbal_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_memory_composite_score_verbal_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 88.6 points with a standard deviation of 7.97. The minimum score was observed to be 56, and the maximum score was observed to be 100.

```{r, include=TRUE}
create_react(baseline_all_positive, user_memory_composite_score_verbal_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_memory_composite_score_verbal_2)
```

### Score Increase Summary

The average point increase from baseline 1 to baseline 2 was observed to be 9.37 points with a standard deviation of 6.76 points. The mininum point increase was observed to be 1, while the maximum point increase was observed to be 44. 

```{r, include=TRUE}
create_react(baseline_all_positive, memory_verbal_diff)
```

### Score Increase Histogram 
```{r, include=TRUE}
score_diff_hist(baseline_all_positive, memory_verbal_diff)
```

### Percent Increase Summary

The average percent increase from baseline 1 to baseline 2 was observed to be a 14.27% increase with a standard deviation of a 11.69% increase.  

```{r, include=TRUE}
react_percent(baseline_all_positive, memory_verbal_percent_inc)
```

### Percent Increase Density Plot
```{r, include=TRUE}
percent_inc_density(baseline_all_positive, memory_verbal_percent_inc)
```


## Verbal Memory Paired *T*-Test Results {.tabset .tabset-fade .tabset-pills}

A paired *T*-test was used to compare the mean verbal memory composite scores of all 18,739 individuals who completed two baseline assessments. On average, individuals scored significantly higher on the second baseline test administration (*M* = 84.74) than the first baseline test administration (*M* = 82.63), *t*(18737) = -26.327, *p* < .01. 
```{r, include=FALSE}

head(mem_verbal_all)

mem_verbal_all_long <- mem_verbal_all %>% 
  pivot_longer(
    cols = c(4:5),
    names_to = "baseline_time",
    names_prefix = "user_memory_composite_score_",
    values_to = "score"
  )

ggplot(mem_verbal_all_long, aes(baseline_time, score)) +
  geom_boxplot() +
    labs(x = "",
         y = "Score")

box_p <- function(df, x, y) {
  ggplot(df, aes({{x}}, {{y}})) +
  geom_boxplot() +
    labs(x = "",
         y = "Score")
}

box_p(mem_verbal_all_long, baseline_time, score)



mem_verbal_1 <- mem_verbal_all$user_memory_composite_score_verbal_1
mem_verbal_2 <- mem_verbal_all$user_memory_composite_score_verbal_2

mem_verbal_res <- t.test(mem_verbal_1, mem_verbal_2, paired = TRUE)

mem_verbal_res

mem_verbal_res$p.value
mem_verbal_res$estimate
mem_verbal_res$statistic

mean_2(mem_verbal_all$user_memory_composite_score_verbal_1)
mean_2(mem_verbal_all$user_memory_composite_score_verbal_2)
```

### Boxplot
```{r, include=TRUE}
box_p(mem_verbal_all_long, baseline_time, score) +
  stat_compare_means(method = "t.test", paired = TRUE, hjust = -0.5)
```

### *T*-Test Results
```{r, include=TRUE}
mem_verbal_res
```

### Baseline 1 Total Descriptive Statistics
```{r, include=TRUE}
create_react(mem_verbal_all, user_memory_composite_score_verbal_1)
```

### Baseline 1 Total Score Histogram
```{r, include=TRUE}
score_hist(mem_verbal_all, user_memory_composite_score_verbal_1)
```

### Baseline 2 Total Descriptive Statistics
```{r, include=TRUE}
create_react(mem_verbal_all, user_memory_composite_score_verbal_2)
```

### Baseline 2 Total Score Histogram
```{r, include=TRUE}
score_hist(mem_verbal_all, user_memory_composite_score_verbal_2)
```


## Visual Memory - Baseline 2 Increase Only {.tabset .tabset-fade .tabset-pills}

11,137 individuals (59.43%) increased their visual memory composite score on the second baseline test administration. 


### Baseline 1 Summary 

The average Baseline 1 score was observed to be 68.33 points with a standard deviation of 12.13. The minimum score was observed to be 22, and the maximum score was observed to be 99.

```{r, include=TRUE}
create_react(mem_visual, user_memory_composite_score_visual_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(mem_visual, user_memory_composite_score_visual_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 80.44 points with a standard deviation of 10.71. The minimum score was observed to be 38, and the maximum score was observed to be 100.

```{r, include=TRUE}
create_react(mem_visual, user_memory_composite_score_visual_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(mem_visual, user_memory_composite_score_visual_2)
```


### Score Increase Summary

The average point increase from baseline 1 to baseline 2 was observed to be 12.1 points with a standard deviation of 8.58 points. The mininum point increase was observed to be 1, while the maximum point increase was observed to be 53. 

```{r visual memory table 1, include=TRUE}
create_react(mem_visual, memory_visual_diff)
```

### Score Increase Histogram 

```{r}
score_diff_hist(mem_visual, memory_visual_diff)
```

### Percent Increase Summary

The average percent increase from baseline 1 to baseline 2 was observed to be a 19.74% increase with a standard deviation of a 17.64% increase.  

```{r visual memory table 2, include=TRUE}
react_percent(mem_visual, memory_visual_percent_inc)
```

### Percent Increase Density Plot
```{r, include=TRUE}
percent_inc_density(mem_visual, memory_visual_percent_inc)
```

## Visual Memory - Increase on all Five Scores {.tabset .tabset-fade .tabset-pills}

This section summarizes the visual memory composite score for the 1,653 individuals who achieved a higher score on all five composite scores of the second baseline test administration.  

### Baseline 1 Summary 

The average Baseline 1 score was observed to be 67.55 points with a standard deviation of 12.2. The minimum score was observed to be 26, and the maximum score was observed to be 95.

```{r, include=TRUE}
create_react(baseline_all_positive, user_memory_composite_score_visual_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_memory_composite_score_visual_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 80.78 points with a standard deviation of 10.32. The minimum score was observed to be 46, and the maximum score was observed to be 100.

```{r, include=TRUE}
create_react(baseline_all_positive, user_memory_composite_score_visual_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_memory_composite_score_visual_2)
```

### Score Increase Summary

The average point increase from baseline 1 to baseline 2 was observed to be 13.23 points with a standard deviation of 9.04 points. The mininum point increase was observed to be 1, while the maximum point increase was observed to be 49. 

```{r, include=TRUE}
create_react(baseline_all_positive, memory_visual_diff)
```

### Score Increase Histogram 
```{r, include=TRUE}
score_diff_hist(baseline_all_positive, memory_visual_diff)
```

### Percent Increase Summary

The average percent increase from baseline 1 to baseline 2 was observed to be a 21.96% increase with a standard deviation of a 19.17% increase.  

```{r, include=TRUE}
react_percent(baseline_all_positive, memory_visual_percent_inc)
```

### Percent Increase Density Plot
```{r, include=TRUE}
percent_inc_density(baseline_all_positive, memory_visual_percent_inc)
```


## Visual Memory Paired *T*-Test Results {.tabset .tabset-fade .tabset-pills}
A paired *T*-test was used to compare the mean visual memory composite scores of all 18,739 individuals who completed two baseline assessments. On average, individuals scored significantly higher on the second baseline test administration (*M* = 76.14) than the first baseline test administration (*M* = 72.5), *t*(18738) = -38.047, *p* < .01. 
```{r, include=FALSE}
mem_visual_all_long <- mem_visual_all %>% 
  pivot_longer(
    cols = c(4:5),
    names_to = "baseline_time",
    names_prefix = "user_memory_composite_score_",
    values_to = "score"
  )


mem_visual_1 <- mem_visual_all$user_memory_composite_score_visual_1
mem_visual_2 <- mem_visual_all$user_memory_composite_score_visual_2

mem_visual_res <- t.test(mem_visual_1, mem_visual_2, paired = TRUE)

mem_visual_res

mean_2(mem_visual_all$user_memory_composite_score_visual_1)
mean_2(mem_visual_all$user_memory_composite_score_visual_2)
```

### Boxplot
```{r, include=TRUE}
box_p(mem_visual_all_long, baseline_time, score) +
  stat_compare_means(method = "t.test", paired = TRUE, hjust = -0.5)
```

### *T*-Test Results
```{r, include=TRUE}
mem_visual_res
```

### Baseline 1 Total Descriptive Statistics
```{r, include=TRUE}
create_react(mem_visual_all, user_memory_composite_score_visual_1)
```

### Baseline 1 Total Score Histogram
```{r, include=TRUE}
score_hist(mem_visual_all, user_memory_composite_score_visual_1)
```

### Baseline 2 Total Descriptive Statistics
```{r, include=TRUE}
create_react(mem_visual_all, user_memory_composite_score_visual_2)
```

### Baseline 2 Total Score Histogram
```{r, include=TRUE}
score_hist(mem_visual_all, user_memory_composite_score_visual_2)
```

## Visual Motor - Baseline 2 Score Increase Only {.tabset .tabset-fade .tabset-pills}

14,355 individuals (76.60%) increased their visual motor composite score on the second baseline test administration. 

### Baseline 1 Summary 

The average Baseline 1 score was observed to be 33.26 points with a standard deviation of 6.46. The minimum score was observed to be 1.13, and the maximum score was observed to be 52.88.

```{r, include=TRUE}
create_react(visual_motor, user_visual_motor_composite_score_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(visual_motor, user_visual_motor_composite_score_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 38.81 points with a standard deviation of 6.3. The minimum score was observed to be 12.05, and the maximum score was observed to be 54.25.

```{r, include=TRUE}
create_react(visual_motor, user_visual_motor_composite_score_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(visual_motor, user_visual_motor_composite_score_2)
```


### Score Increase Summary

The average point increase from baseline 1 to baseline 2 was observed to be 5.55 points with a standard deviation of 3.97 points. The mininum point increase was observed to be 0.02, while the maximum point increase was observed to be 37.35. 

```{r visual motor table 1, include=TRUE}
create_react(visual_motor, visual_motor_diff)
```

### Score Increase Histogram 

```{r}
score_diff_hist(visual_motor, visual_motor_diff)
```

### Percent Increase Summary

The average percent increase from baseline 1 to baseline 2 was observed to be a 18.8% increase with a standard deviation of a 22.17% increase.  

```{r visual motor table 2, include=TRUE}
react_percent(visual_motor, visual_motor_percent_inc)
```

### Percent Increase Density Plot
```{r, include=TRUE}
percent_inc_density(visual_motor, visual_motor_percent_inc)
```

## Visual Motor - Increase on all Five Scores {.tabset .tabset-fade .tabset-pills}

This section summarizes the reaction time composite score for the 1,653 individuals who achieved a higher score on all five composite scores of the second baseline test administration.  

### Baseline 1 Summary 

The average Baseline 1 score was observed to be 32.15 points with a standard deviation of 6.26. The minimum score was observed to be 11.75, and the maximum score was observed to be 50.13.

```{r, include=TRUE}
create_react(baseline_all_positive, user_visual_motor_composite_score_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_visual_motor_composite_score_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 38.7 points with a standard deviation of 6.12. The minimum score was observed to be 13.3, and the maximum score was observed to be 53.25.

```{r, include=TRUE}
create_react(baseline_all_positive, user_visual_motor_composite_score_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_visual_motor_composite_score_2)
```


### Score Increase Summary

The average point increase from baseline 1 to baseline 2 was observed to be 6.56 points with a standard deviation of 4.21 points. The mininum point increase was observed to be 0.02, while the maximum point increase was observed to be 32.55. 

```{r, include=TRUE}
create_react(baseline_all_positive, visual_motor_diff)
```

### Score Increase Histogram 
```{r, include=TRUE}
score_diff_hist(baseline_all_positive, visual_motor_diff)
```

### Percent Increase Summary

The average percent increase from baseline 1 to baseline 2 was observed to be a 22.82% increase with a standard deviation of a 21.77% increase.  

```{r, include=TRUE}
react_percent(baseline_all_positive, visual_motor_percent_inc)
```

### Percent Increase Density Plot
```{r, include=TRUE}
percent_inc_density(baseline_all_positive, visual_motor_percent_inc)
```


## Visual Motor Paired *T*-Test Results {.tabset .tabset-fade .tabset-pills}
A paired *T*-test was used to compare the reaction time composite scores of all 18,739 individuals who completed two baseline assessments. On average, individuals scored significantly higher on the second baseline test administration (*M* = 37.64) than the first baseline test administration (*M* = 34.15), *t*(18738) = -89.275, *p* < .01. 
```{r, include=FALSE}
visual_motor_all_long <- visual_motor_all %>% 
  pivot_longer(
    cols = c(4:5),
    names_to = "baseline_time",
    names_prefix = "user_visual_motor_composite_",
    values_to = "score"
  )


visual_motor_1 <- visual_motor_all$user_visual_motor_composite_score_1
visual_motor_2 <- visual_motor_all$user_visual_motor_composite_score_2

visual_motor_res <- t.test(visual_motor_1, visual_motor_2, paired = TRUE)

visual_motor_res

mean_2(visual_motor_all$user_visual_motor_composite_score_1)
mean_2(visual_motor_all$user_visual_motor_composite_score_2)
```

### Boxplot
```{r, include=TRUE}
box_p(visual_motor_all_long, baseline_time, score) +
  stat_compare_means(method = "t.test", paired = TRUE, hjust = -0.5)
```

### *T*-Test Results
```{r, include=TRUE}
visual_motor_res
```

### Baseline 1 Total Descriptive Statistics
```{r, include=TRUE}
create_react(visual_motor_all, user_visual_motor_composite_score_1)
```

### Baseline 1 Total Score Histogram
```{r, include=TRUE}
score_hist(visual_motor_all, user_visual_motor_composite_score_1)
```

### Baseline 2 Total Descriptive Statistics
```{r, include=TRUE}
create_react(visual_motor_all, user_visual_motor_composite_score_2)
```

### Baseline 2 Total Score Histogram
```{r, include=TRUE}
score_hist(visual_motor_all, user_visual_motor_composite_score_2)
```


## Impulse Control - Baseline 2 Score Increase Only {.tabset .tabset-fade .tabset-pills}

9,023 individuals (48.15%) increased their impulse control composite score on the second baseline test administration. 

### Baseline 1 Summary 

The average Baseline 1 score was observed to be 9.64 points with a standard deviation of 5.36. The minimum score was observed to be 1, and the maximum score was observed to be 30.

```{r, include=TRUE}
create_react(impulse_control, user_impulse_control_composite_score_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(impulse_control, user_impulse_control_composite_score_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 5.14 points with a standard deviation of 3.6. The minimum score was observed to be 0, and the maximum score was observed to be 27.

```{r, include=TRUE}
create_react(impulse_control, user_impulse_control_composite_score_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(impulse_control, user_impulse_control_composite_score_2)
```


### Score Increase Summary

The average point increase from baseline 1 to baseline 2 was observed to be 4.5 points with a standard deviation of 3.76 points. The mininum point increase was observed to be 1, while the maximum point increase was observed to be 27. 

```{r impulse control table 1, include=TRUE}
create_react(impulse_control, impulse_control_diff)
```

### Score Increase Histogram 

```{r}
score_diff_hist(impulse_control, impulse_control_diff)
```

### Percent Increase Summary

The average percent increase from baseline 1 to baseline 2 was observed to be a 46.68% increase with a standard deviation of 23.37% increase.

```{r impulse control table 2, include=TRUE}
react_percent(impulse_control, impulse_control_percent_dec)
```

### Percent Increase Density Plot
```{r, include=TRUE}
percent_inc_density(impulse_control, impulse_control_percent_dec)
```

## Impulse Control - Increase on all Five Scores {.tabset .tabset-fade .tabset-pills}

This section summarizes the impulse control composite score for the 1,653 individuals who achieved a higher score on all five composite scores of the second baseline test administration. 

### Baseline 1 Summary 

The average Baseline 1 score was observed to be 9.98 points with a standard deviation of 5.58. The minimum score was observed to be 1, and the maximum score was observed to be 30.

```{r, include=TRUE}
create_react(baseline_all_positive, user_impulse_control_composite_score_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_impulse_control_composite_score_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 5.18 points with a standard deviation of 3.55. The minimum score was observed to be 0, and the maximum score was observed to be 26.

```{r, include=TRUE}
create_react(baseline_all_positive, user_impulse_control_composite_score_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_impulse_control_composite_score_2)
```


### Score Increase Summary

The average point increase from baseline 1 to baseline 2 was observed to be 4.79 points with a standard deviation of 4.08 points. The mininum point increase was observed to be 1, while the maximum point increase was observed to be 25. 

```{r, include=TRUE}
create_react(baseline_all_positive, impulse_control_diff)
```

### Score Increase Histogram 
```{r, include=TRUE}
score_diff_hist(baseline_all_positive, impulse_control_diff)
```

### Percent Increase Summary

The average percent increase from baseline 1 to baseline 2 was observed to be a 47.13% increase with a standard deviation of a 23.26% increase.

```{r, include=TRUE}
react_percent(baseline_all_positive, impulse_control_percent_dec)
```

### Percent Increase Density Plot
```{r, include=TRUE}
percent_inc_density(baseline_all_positive, impulse_control_percent_dec)
```


## Impulse Control Paired *T*-Test Results {.tabset .tabset-fade .tabset-pills}
A paired *T*-test was used to compare the impulse control composite scores of all 18,739 individuals who completed two baseline assessments. On average, individuals scored significantly higher on the first baseline test administration (*M* = 7.41) than the second baseline test administration (*M* = 6.99), *t*(18738) = 10.641, *p* < .001.

```{r, include=FALSE}
impulse_control_all_long <- impulse_control_all %>% 
  pivot_longer(
    cols = c(4:5),
    names_to = "baseline_time",
    names_prefix = "user_impulse_control_composite_",
    values_to = "score"
  )


impulse_control_1 <- impulse_control_all$user_impulse_control_composite_score_1
impulse_control_2 <- impulse_control_all$user_impulse_control_composite_score_2

impulse_control_res <- t.test(impulse_control_1, impulse_control_2, paired = TRUE)

impulse_control_res

mean_2(impulse_control_all$user_impulse_control_composite_score_1)
mean_2(impulse_control_all$user_impulse_control_composite_score_2)
```

### Boxplot
```{r, include=TRUE}
box_p(impulse_control_all_long, baseline_time, score) +
  stat_compare_means(method = "t.test", paired = TRUE, hjust = -0.5)
```

### *T*-Test Results
```{r, include=TRUE}
impulse_control_res
```

### Baseline 1 Total Descriptive Statistics
```{r, include=TRUE}
create_react(impulse_control_all, user_impulse_control_composite_score_1)
```

### Baseline 1 Total Score Histogram
```{r, include=TRUE}
score_hist(impulse_control_all, user_impulse_control_composite_score_1)
```

### Baseline 2 Total Descriptive Statistics
```{r, include=TRUE}
create_react(impulse_control_all, user_impulse_control_composite_score_2)
```

### Baseline 2 Total Score Histogram
```{r, include=TRUE}
score_hist(impulse_control_all, user_impulse_control_composite_score_2)
```


## Reaction Time - Baseline 2 Score Increase Only {.tabset .tabset-fade .tabset-pills}

11,084 individuals (59.15%) improved their reaction time composite score on the second baseline test administration. 

### Baseline 1 Summary 

The average Baseline 1 score was observed to be 0.67 points with a standard deviation of 0.11. The minimum score (indicating faster reaction time) was observed to be 0.44, and the maximum score (indicating slower reaction time) was observed to be 2.85.

```{r, include=TRUE}
create_react(reaction_time, user_reaction_time_composite_score_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(reaction_time, user_reaction_time_composite_score_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 0.59 points with a standard deviation of 0.07. The minimum score was observed to be -0.18, and the maximum score was observed to be 1.03.

```{r, include=TRUE}
create_react(reaction_time, user_reaction_time_composite_score_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(reaction_time, user_reaction_time_composite_score_2)
```


### Score Increase Summary

The average point decrease (indicating better performance for the reaction time composite test) from baseline 1 to baseline 2 was observed to be 0.08 points with a standard deviation of 0.08 points. The mininum point decrease (indicative of better performance) was observed to be 0.01, while the maximum point decrease was observed to be 2.36. 

```{r reaction time table 1, include=TRUE}
create_react(reaction_time, reaction_time_diff)
```

### Score Increase Histogram 

```{r}
ggplot(reaction_time, aes(reaction_time_diff)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  labs(x = "Point Decrease on Baseline 2",
       y = "Number of Individuals")
```

### Percent Increase Summary

The average percent decrease from baseline 1 to baseline 2 was observed to be a 11.36% increase with a standard deviation of a 8.36% decrease.  

```{r reaction time table 2, include=TRUE}
react_percent(reaction_time, reaction_time_percent_dec)
```

### Percent Increase Density Plot
```{r, include=TRUE}
ggplot(reaction_time, aes(reaction_time_percent_dec)) +
  geom_density(fill = "#56B4E9",
               bw = 15) +
  scale_x_continuous("Percent Decrease on Baseline 2", labels = function(x) paste0(x, "%")) +
    labs(x = "Percent Decrease on Baseline 2",
         y = "Density")
```

## Reaction Time - Increase on all Five Scores {.tabset .tabset-fade .tabset-pills}

This section summarizes the reaction time composite score for the 1,653 individuals who achieved a higher score on all five composite scores of the second baseline test administration.  

### Baseline 1 Summary 

The average Baseline 1 score was observed to be 0.67 points with a standard deviation of 0.11. The minimum score was observed to be 0.46 (indicative of faster reaction time), and the maximum score was observed to be 1.89.

```{r, include=TRUE}
create_react(baseline_all_positive, user_reaction_time_composite_score_1)
```

### Baseline 1 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_reaction_time_composite_score_1)
```

### Baseline 2 Summary 

The average Baseline 2 score was observed to be 0.59 points with a standard deviation of 0.07. The minimum score was observed to be 0.41, and the maximum score was observed to be 0.9.

```{r, include=TRUE}
create_react(baseline_all_positive, user_reaction_time_composite_score_2)
```

### Baseline 2 Histogram

```{r, include=TRUE}
score_hist(baseline_all_positive, user_reaction_time_composite_score_2)
```


### Score Increase Summary

The average point decrease from baseline 1 to baseline 2 was observed to be 0.08 points with a standard deviation of 0.08 points. The mininum point decrease was observed to be 0.01, while the maximum point decrease was observed to be 1.08. 

```{r, include=TRUE}
create_react(baseline_all_positive, reaction_time_diff)
```

### Score Increase Histogram 
```{r, include=TRUE}
ggplot(baseline_all_positive, aes(reaction_time_diff)) +
  geom_histogram(fill = "#56B4E9",
                color = "white", 
                alpha = 0.9,
                bins = 25) +
  labs(x = "Point Decrease on Baseline 2",
       y = "Number of Individuals")
```

### Percent Increase Summary

The average percent decrease from baseline 1 to baseline 2 was observed to be a 11.33% decrease with a standard deviation of a 8.33% decrease.  

```{r, include=TRUE}
react_percent(baseline_all_positive, reaction_time_percent_dec)
```

### Percent Increase Density Plot
```{r, include=TRUE}
ggplot(baseline_all_positive, aes(reaction_time_percent_dec)) +
  geom_density(fill = "#56B4E9",
               bw = 15) +
  scale_x_continuous("Percent Decrease on Baseline 2", labels = function(x) paste0(x, "%")) +
    labs(x = "Percent Decrease on Baseline 2",
         y = "Density")
```


## Reaction Time Paired *T*-Test Results {.tabset .tabset-fade .tabset-pills}
A paired *T*-test was used to compare the reaction time composite scores of all 18,739 individuals who completed two baseline assessments. On average, individuals demonstrated a faster reaction time on the second baseline test administration (*M* = 0.62) than the first baseline test administration (*M* = 0.64), *t*(18737) = 27.658, *p* < .01. 
```{r, include=FALSE}
reaction_time_all_long <- reaction_time_all %>% 
  pivot_longer(
    cols = c(4:5),
    names_to = "baseline_time",
    names_prefix = "user_reaction_time_composite_",
    values_to = "score"
  )


reaction_time_1 <- reaction_time_all$user_reaction_time_composite_score_1
reaction_time_2 <- reaction_time_all$user_reaction_time_composite_score_2

reaction_time_res <- t.test(reaction_time_1, reaction_time_2, paired = TRUE)

reaction_time_res

mean_2(reaction_time_all$user_reaction_time_composite_score_1)
mean_2(reaction_time_all$user_reaction_time_composite_score_2)
```

### Boxplot
```{r, include=TRUE}
box_p(reaction_time_all_long, baseline_time, score) +
  stat_compare_means(method = "t.test", paired = TRUE, hjust = -0.5)
```

### *T*-Test Results
```{r, include=TRUE}
reaction_time_res
```

### Baseline 1 Total Descriptive Statistics
```{r, include=TRUE}
create_react(reaction_time_all, user_reaction_time_composite_score_1)
```

### Baseline 1 Total Score Histogram
```{r, include=TRUE}
score_hist(reaction_time_all, user_reaction_time_composite_score_1)
```

### Baseline 2 Total Descriptive Statistics
```{r, include=TRUE}
create_react(reaction_time_all, user_reaction_time_composite_score_2)
```

### Baseline 2 Total Score Histogram
```{r, include=TRUE}
score_hist(reaction_time_all, user_reaction_time_composite_score_2)
```


# What is the relationship between age and point increase on baseline testing? {.tabset .tabset-fade .tabset-pills}

To explore the relationship between age and point increase on baseline testing, indivuals ages 10-18 on both baseline tests were included from the sample of individuals who achieved positive gain on at least one baseline test domain. This new sample consists of 18,371 individuals. 

```{r, include=FALSE}
head(baseline_final)

baseline_age <- baseline_final %>% 
  filter(user_age_1 %in% (10:18),
         user_age_2 %in% (10:18))

baseline_age_factor <- baseline_age %>% 
  mutate(user_age_1 = as.factor(user_age_1),
         user_age_2 = as.factor(user_age_2))
```

## Verbal Memory {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Score Plot

```{r, include=FALSE}
ggplot(baseline_age, aes(user_memory_composite_score_verbal_1, user_age_1)) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Score",
       y = "Age")

score_scatter <- function(df, x, y) {
  ggplot(df, aes({{x}}, {{y}})) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Score",
       y = "Age")
}

point_increase_scatter <- function(df, x, y) {
  ggplot(df, aes({{x}}, {{y}})) +
  geom_point(alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Point Increase on Baseline 2",
       y = "Age")
}
```

```{r, include=TRUE}
score_scatter(baseline_age, user_memory_composite_score_verbal_1, user_age_1)
```

### Baseline 2 Score Plot

```{r, include=TRUE}
score_scatter(baseline_age, user_memory_composite_score_verbal_2, user_age_2)
```

### Baseline Point Increase

```{r, include=TRUE}
point_increase_scatter(baseline_age, memory_verbal_diff, user_age_2)
```

### Baseline 1 Model 

On average, 10 year olds obtained a score of 78.03. On average:

  * Age 11 scored 1.08 points higher
  * Age 12 scored .50 points higher
  * Age 13 scored 0.99 points higher
  * Age 14 scored 1.22 points higher
  * Age 15 scored 1.49 points higher
  * Age 16 scored 1.49 points higher
  * Age 17 scored 9.70 points lower
  
None of these differences in performance are significantly different. 

```{r, include=TRUE}
mem_verbal_mod_1 <- lm(user_memory_composite_score_verbal_1 ~ user_age_1, data = baseline_age_factor)

summary(mem_verbal_mod_1)
```

### Baseline 2 Model 

On average, scores increase with age, but none of the differences between ages are significantly different.

```{r, include=TRUE}
mem_verbal_mod_2 <- lm(user_memory_composite_score_verbal_2 ~ user_age_2, data = baseline_age_factor)

summary(mem_verbal_mod_2)
```

### Score Increase Model 

On average, individuals age 10 at the time of the second baseline test increased their score by 8.75 points. The only significant difference in this model is that, on average, individuals age 18 at the time of the second baseline test experienced a point gain 9.92 points higher than the gain of 10 year olds. 

```{r, include=TRUE}
mem_verbal_diff_baseline_mod <- lm(memory_verbal_diff ~ user_age_2, data = baseline_age_factor)

summary(mem_verbal_diff_baseline_mod)
```

## Visual Memory {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Score Plot

```{r, include=TRUE}
score_scatter(baseline_age, user_memory_composite_score_visual_1, user_age_1)
```

### Baseline 2 Score Plot

```{r, include=TRUE}
score_scatter(baseline_age, user_memory_composite_score_visual_2, user_age_2)
```

### Baseline Point Increase

```{r, include=TRUE}
point_increase_scatter(baseline_age, memory_visual_diff, user_age_2)
```

### Baseline 1 Model 

On average, 10 year olds obtained a score of 66.97. Significant differences include:

  * On average, individuals age 11 scored 1.77 points higher (*p* = .04)
  * On average, individuals age 14 scored 1.74 points higher (*p* = .03)

```{r, include=TRUE}
mem_visual_mod_1 <- lm(user_memory_composite_score_visual_1 ~ user_age_1, data = baseline_age_factor)

summary(mem_visual_mod_1)
```

### Baseline 2 Model 

No significant differences in model. 

```{r, include=TRUE}
mem_visual_mod_2 <- lm(user_memory_composite_score_visual_2 ~ user_age_2, data = baseline_age_factor)

summary(mem_visual_mod_2)
```

### Score Increase Model 

No significant differences in model. 

```{r, include=TRUE}
mem_visual_diff_baseline_mod <- lm(memory_visual_diff ~ user_age_2, data = baseline_age_factor)

summary(mem_visual_diff_baseline_mod)
```

## Visual Motor {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Score Plot

```{r, include=TRUE}
score_scatter(baseline_age, user_visual_motor_composite_score_1, user_age_1)
```

### Baseline 2 Score Plot

```{r, include=TRUE}
score_scatter(baseline_age, user_visual_motor_composite_score_2, user_age_2)
```

### Baseline Point Increase

```{r, include=TRUE}
point_increase_scatter(baseline_age, visual_motor_diff, user_age_2)
```

### Baseline 1 Model 

This model is sigificant. The age coefficient accounts for 2.1% of the variability in scores. On average, individuals age 10 obtained a score of 29.89. The following differences are significant. On average:

  * Age 11 scored 1.48 points higher (*p* = .0001)
  * Age 12 scored 2.85 points higher (*p* < .0001)
  * Age 13 scored 3.67 points higher (*p* < .0001)
  * Age 14 scored 4.32 points higher (*p* < .0001)
  * Age 15 scored 4.27 points higher (*p* < .0001)
  * Age 16 scored 4.43 points higher (*p* < .0001)
  * Age 17 scored 11.91 points higher (*p* = .008)

```{r, include=TRUE}
visual_motor_mod_1 <- lm(user_visual_motor_composite_score_1 ~ user_age_1, data = baseline_age_factor)

summary(visual_motor_mod_1)
```

### Baseline 2 Model 

Some significant differences in the model. Individuals age 10, on average, obtained a score of 34.07. Significant differences include, on aveage:

  * Individuals age 15 scored 5.13 points higher (*p* = .03)
  * Individuals age 16 scored 5.18 points higher (*p* = .03)

```{r, include=TRUE}
visual_motor_mod_2 <- lm(user_visual_motor_composite_score_2 ~ user_age_2, data = baseline_age_factor)

summary(visual_motor_mod_2)
```

### Score Increase Model 

No significant differences in model. 

```{r, include=TRUE}
visual_motor_diff_baseline_mod <- lm(visual_motor_diff ~ user_age_2, data = baseline_age_factor)

summary(visual_motor_diff_baseline_mod)
```


## Impulse Control {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Score Plot

```{r, include=TRUE}
score_scatter(baseline_age, user_impulse_control_composite_score_1, user_age_1)
```

### Baseline 2 Score Plot

```{r, include=TRUE}
score_scatter(baseline_age, user_impulse_control_composite_score_2, user_age_2)
```

### Baseline Point Increase

```{r, include=TRUE}
point_increase_scatter(baseline_age, impulse_control_diff, user_age_2)
```

### Baseline 1 Model 

On average, individuals age 10 obtained a score of 10.86. The following differences are significant. On average:

  * Age 12 scored 0.89 points lower (better performance) (*p* = .04)
  * Age 13 scored 1.25 points lower (*p* = .002)
  * Age 14 scored 1.58 points lower (*p* = .0001)
  * Age 15 scored 1.88 points lower (*p* = .0001)
  * Age 16 scored 3.17 points lower (*p* = .0001)
  

```{r, include=TRUE}
impulse_control_mod_1 <- lm(user_impulse_control_composite_score_1 ~ user_age_1, data = baseline_age_factor)

summary(impulse_control_mod_1)
```

### Baseline 2 Model 

No significant differences in model. 

```{r, include=TRUE}
impulse_control_mod_2 <- lm(user_impulse_control_composite_score_2 ~ user_age_2, data = baseline_age_factor)

summary(impulse_control_mod_2)
```

### Score Increase Model 

No significant differences in model. 

```{r, include=TRUE}
impulse_control_diff_baseline_mod <- lm(impulse_control_diff ~ user_age_2, data = baseline_age_factor)

summary(impulse_control_diff_baseline_mod)
```

## Reaction Time {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Score Plot

```{r, include=TRUE}
score_scatter(baseline_age, user_reaction_time_composite_score_1, user_age_1)
```

### Baseline 2 Score Plot

```{r, include=TRUE}
score_scatter(baseline_age, user_reaction_time_composite_score_2, user_age_2)
```

### Baseline Point Increase

```{r, include=TRUE}
point_increase_scatter(baseline_age, reaction_time_diff, user_age_2)
```

### Baseline 1 Model 

On average, individuals age 10 obtained a score of 0.72. The following differences are significant. On average:

  * Age 11 scored 0.02 points lower (better performance) (*p* = .01)
  * Age 12 scored 0.05 points lower (*p* < .0001)
  * Age 13 scored 0.06 points lower (*p* < .0001)
  * Age 14 scored 0.07 points lower (*p* < .0001)
  * Age 15 scored 0.07 points lower (*p* < .0001)
  * Age 16 scored 0.05 points lower (*p* = .002)
  

```{r, include=TRUE}
reaction_time_mod_1 <- lm(user_reaction_time_composite_score_1 ~ user_age_1, data = baseline_age_factor)

summary(reaction_time_mod_1)
```

### Baseline 2 Model 

On average, individuals age 10 obtained a score of 0.69. The following differences are significant. On average:

  * Age 12 scored 0.07 points lower (better performance) (*p* = .0003)
  * Age 13 scored 0.09 points lower (*p* < .0001)
  * Age 14 scored 0.10 points lower (*p* < .0001)
  * Age 15 scored 0.11 points lower (*p* < .0001)
  * Age 16 scored 0.11 points lower (*p* < .0001)
  * Age 17 scored 0.10 points lower (*p* < .0001)

```{r, include=TRUE}
reaction_time_mod_2 <- lm(user_reaction_time_composite_score_2 ~ user_age_2, data = baseline_age_factor)

summary(reaction_time_mod_2)
```

### Score Increase Model 

No significant differences in model. 

```{r, include=TRUE}
reaction_time_diff_baseline_mod <- lm(reaction_time_diff ~ user_age_2, data = baseline_age_factor)

summary(reaction_time_diff_baseline_mod)
```

# What is the relationship between school attended and point increase on baseline testing? {.tabset .tabset-fade .tabset-pills}

To explore the relationship between school attended and point increase on baseline testing, schools with 100 or more individuals who completed two baseline tests were included from the sample of individuals who achieved positive gain on at least one baseline test domain. This new sample consists of 17,641 individuals. 

```{r, include=FALSE}
head(baseline_final)

baseline_final %>% 
  count(org_name_1) 

baseline_final %>% 
  count(org_name_2) 

baseline_school_1 <- baseline_final

baseline_school_1_count <- baseline_final %>% 
  count(org_name_1) %>% 
  filter(n >= 100)

baseline_school_1 <- baseline_school_1 %>% 
  filter(org_name_1 %in% baseline_school_1_count$org_name_1)

b_check <- baseline_school_1 %>% 
  group_by(org_name_1) %>% 
  summarize(total = n())

baseline_school_2 <- baseline_final

baseline_school_2_count <- baseline_final %>% 
  count(org_name_2) %>% 
  filter(n >= 100)

baseline_school_2 <- baseline_school_2 %>% 
  filter(org_name_2 %in% baseline_school_2_count$org_name_2)

baseline_school <- full_join(baseline_school_1, baseline_school_2)
```

## Verbal Memory {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
mem_verbal_mod_1_school <- lm(user_memory_composite_score_verbal_1 ~ org_name_1, data = baseline_school)

summary(mem_verbal_mod_1_school)
```

### Baseline 2 Model 

```{r, include=TRUE}
mem_verbal_mod_2_school <- lm(user_memory_composite_score_verbal_2 ~ org_name_2, data = baseline_school)

summary(mem_verbal_mod_2_school)
```

### Score Increase Model 

```{r, include=TRUE}
mem_verbal_diff_baseline_mod_school <- lm(memory_verbal_diff ~ org_name_2, data = baseline_school)

summary(mem_verbal_diff_baseline_mod_school)
```

## Visual Memory {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
mem_visual_mod_1_school <- lm(user_memory_composite_score_visual_1 ~ org_name_1, data = baseline_school)

summary(mem_visual_mod_1_school)
```

### Baseline 2 Model 

```{r, include=TRUE}
mem_visual_mod_2_school <- lm(user_memory_composite_score_visual_2 ~ org_name_2, data = baseline_school)

summary(mem_visual_mod_2_school)
```

### Score Increase Model 

No significant differences in model. 

```{r, include=TRUE}
mem_visual_diff_baseline_mod_school <- lm(memory_visual_diff ~ org_name_2, data = baseline_school)

summary(mem_visual_diff_baseline_mod_school)
```

## Visual Motor {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

This model has multiple significant differences between schools. 

```{r, include=TRUE}
visual_motor_mod_1_school <- lm(user_visual_motor_composite_score_1 ~ org_name_1, data = baseline_school)

summary(visual_motor_mod_1_school)
```

### Baseline 2 Model 

This model has multiple significant differences between schools. 

```{r, include=TRUE}
visual_motor_mod_2_school <- lm(user_visual_motor_composite_score_2 ~ org_name_2, data = baseline_school)

summary(visual_motor_mod_2_school)
```

### Score Increase Model 

No significant differences in model. 

```{r, include=TRUE}
visual_motor_diff_baseline_mod_school <- lm(visual_motor_diff ~ org_name_2, data = baseline_school)

summary(visual_motor_diff_baseline_mod_school)
```


## Impulse Control {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
impulse_control_mod_1_school <- lm(user_impulse_control_composite_score_1 ~ org_name_1, data = baseline_school)

summary(impulse_control_mod_1_school)
```

### Baseline 2 Model 

```{r, include=TRUE}
impulse_control_mod_2_school <- lm(user_impulse_control_composite_score_2 ~ org_name_2, data = baseline_school)

summary(impulse_control_mod_2_school)
```

### Score Increase Model 

```{r, include=TRUE}
impulse_control_diff_baseline_mod_school <- lm(impulse_control_diff ~ org_name_2, data = baseline_school)

summary(impulse_control_diff_baseline_mod_school)
```

## Reaction Time {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
reaction_time_mod_1_school <- lm(user_reaction_time_composite_score_1 ~ org_name_1, data = baseline_school)

summary(reaction_time_mod_1_school)
```

### Baseline 2 Model 

```{r, include=TRUE}
reaction_time_mod_2_school <- lm(user_reaction_time_composite_score_2 ~ org_name_2, data = baseline_school)

summary(reaction_time_mod_2_school)
```

### Score Increase Model 

```{r, include=TRUE}
reaction_time_diff_baseline_mod_school <- lm(reaction_time_diff ~ org_name_2, data = baseline_school)

summary(reaction_time_diff_baseline_mod_school)
```

# What is the relationship between sport played and point increase on baseline testing? {.tabset .tabset-fade .tabset-pills}

To explore the relationship between sport played and point increase on baseline testing, sports with 400 or more individuals who completed two baseline tests were included from the sample of individuals who achieved positive gain on at least one baseline test domain. This new sample consists of 15,520 individuals. 

```{r, include=FALSE}
head(baseline_final)

baseline_final %>% 
  count(user_current_sport_1) 

baseline_final %>% 
  count(user_current_sport_2) 

baseline_sport_1 <- baseline_final

baseline_sport_1_count <- baseline_final %>% 
  count(user_current_sport_1) %>% 
  filter(n >= 400)

baseline_sport_1 <- baseline_sport_1 %>% 
  filter(user_current_sport_1 %in% baseline_sport_1_count$user_current_sport_1)

b_check_2 <- baseline_sport_1 %>% 
  group_by(user_current_sport_1) %>% 
  summarize(total = n())

baseline_sport_2 <- baseline_final

baseline_sport_2_count <- baseline_final %>% 
  count(user_current_sport_2) %>% 
  filter(n >= 400)

baseline_sport_2 <- baseline_sport_2 %>% 
  filter(user_current_sport_2 %in% baseline_sport_2_count$user_current_sport_2)

b_check_3 <- baseline_sport_2 %>% 
  group_by(user_current_sport_2) %>% 
  summarize(total = n())

baseline_sport <- full_join(baseline_school_1, baseline_school_2)

baseline_sport <- baseline_sport %>% 
  filter(user_current_sport_1 != "Skipped",
         user_current_sport_2 != "Skipped")
```

## Verbal Memory {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
mem_verbal_mod_1_sport <- lm(user_memory_composite_score_verbal_1 ~ user_current_sport_1, data = baseline_sport)

summary(mem_verbal_mod_1_sport)
```

### Baseline 2 Model 

```{r, include=TRUE}
mem_verbal_mod_2_sport <- lm(user_memory_composite_score_verbal_2 ~ user_current_sport_2, data = baseline_sport)

summary(mem_verbal_mod_2_sport)
```

### Score Increase Model 

```{r, include=TRUE}
mem_verbal_diff_baseline_mod_sport <- lm(memory_verbal_diff ~ user_current_sport_2, data = baseline_sport)

summary(mem_verbal_diff_baseline_mod_sport)
```

## Visual Memory {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
mem_visual_mod_1_sport <- lm(user_memory_composite_score_visual_1 ~ user_current_sport_1, data = baseline_sport)

summary(mem_visual_mod_1_sport)
```

### Baseline 2 Model 

```{r, include=TRUE}
mem_visual_mod_2_sport <- lm(user_memory_composite_score_visual_2 ~ user_current_sport_2, data = baseline_sport)

summary(mem_visual_mod_2_sport)
```

### Score Increase Model 

```{r, include=TRUE}
mem_visual_diff_baseline_mod_sport <- lm(memory_visual_diff ~ user_current_sport_2, data = baseline_sport)

summary(mem_visual_diff_baseline_mod_sport)
```

## Visual Motor {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
visual_motor_mod_1_sport <- lm(user_visual_motor_composite_score_1 ~ user_current_sport_1, data = baseline_sport)

summary(visual_motor_mod_1_sport)
```

### Baseline 2 Model 

```{r, include=TRUE}
visual_motor_mod_2_sport <- lm(user_visual_motor_composite_score_2 ~ user_current_sport_2, data = baseline_sport)

summary(visual_motor_mod_2_sport)
```

### Score Increase Model 

```{r, include=TRUE}
visual_motor_diff_baseline_mod_sport <- lm(visual_motor_diff ~ user_current_sport_2, data = baseline_sport)

summary(visual_motor_diff_baseline_mod_sport)
```


## Impulse Control {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
impulse_control_mod_1_sport <- lm(user_impulse_control_composite_score_1 ~ user_current_sport_1, data = baseline_sport)

summary(impulse_control_mod_1_sport)
```

### Baseline 2 Model 

```{r, include=TRUE}
impulse_control_mod_2_sport <- lm(user_impulse_control_composite_score_2 ~ user_current_sport_2, data = baseline_sport)

summary(impulse_control_mod_2_sport)
```

### Score Increase Model 

```{r, include=TRUE}
impulse_control_diff_baseline_mod_sport <- lm(impulse_control_diff ~ user_current_sport_2, data = baseline_sport)

summary(impulse_control_diff_baseline_mod_sport)
```

## Reaction Time {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
reaction_time_mod_1_sport <- lm(user_reaction_time_composite_score_1 ~ user_current_sport_1, data = baseline_sport)

summary(reaction_time_mod_1_sport)
```

### Baseline 2 Model 

```{r, include=TRUE}
reaction_time_mod_2_sport <- lm(user_reaction_time_composite_score_2 ~ user_current_sport_2, data = baseline_sport)

summary(reaction_time_mod_2_sport)
```

### Score Increase Model 

```{r, include=TRUE}
reaction_time_diff_baseline_mod_sport <- lm(reaction_time_diff ~ user_current_sport_2, data = baseline_sport)

summary(reaction_time_diff_baseline_mod_sport)
```

# What is the relationship between age, sport played, and school attended and point increase on baseline testing? {.tabset .tabset-fade .tabset-pills}

The entire sample of 18,395 individuals who obtained positive gain on at least one baseline 2 domain was utilzed to conduct a multiple regression analysis.

## Verbal Memory {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
mem_verbal_mod_1_all <- lm(user_memory_composite_score_verbal_1 ~ user_age_1 + org_name_1 + user_current_sport_1, data = baseline_final)

summary(mem_verbal_mod_1_all)
```

### Baseline 2 Model 

```{r, include=TRUE}
mem_verbal_mod_2_all <- lm(user_memory_composite_score_verbal_2 ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(mem_verbal_mod_2_all)
```

### Score Increase Model 

```{r, include=TRUE}
mem_verbal_diff_baseline_mod_all <- lm(memory_verbal_diff ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(mem_verbal_diff_baseline_mod_all)
```

## Visual Memory {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
mem_visual_mod_1_all <- lm(user_memory_composite_score_visual_1 ~ user_age_1 + org_name_1 + user_current_sport_1, data = baseline_final)

summary(mem_visual_mod_1_all)
```

### Baseline 2 Model 

```{r, include=TRUE}
mem_visual_mod_2_all <- lm(user_memory_composite_score_visual_2 ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(mem_visual_mod_2_all)
```

### Score Increase Model 

```{r, include=TRUE}
mem_visual_diff_baseline_mod_all <- lm(memory_visual_diff ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(mem_visual_diff_baseline_mod_all)
```

## Visual Motor {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
visual_motor_mod_1_all <- lm(user_visual_motor_composite_score_1 ~ user_age_1 + org_name_1 + user_current_sport_1, data = baseline_final)

summary(visual_motor_mod_1_all)
```

### Baseline 2 Model 

```{r, include=TRUE}
visual_motor_mod_2_all <- lm(user_visual_motor_composite_score_2 ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(visual_motor_mod_2_all)
```

### Score Increase Model 

```{r, include=TRUE}
visual_motor_diff_baseline_mod_all <- lm(visual_motor_diff ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(visual_motor_diff_baseline_mod_all)
```


## Impulse Control {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
impulse_control_mod_1_all <- lm(user_impulse_control_composite_score_1 ~ user_age_1 + org_name_1 + user_current_sport_1, data = baseline_final)

summary(impulse_control_mod_1_all)
```

### Baseline 2 Model 

```{r, include=TRUE}
impulse_control_mod_2_all <- lm(user_impulse_control_composite_score_2 ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(impulse_control_mod_2_all)
```

### Score Increase Model 

```{r, include=TRUE}
impulse_control_diff_baseline_mod_all <- lm(impulse_control_diff ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(impulse_control_diff_baseline_mod_all)
```

## Reaction Time {.tabset .tabset-fade .tabset-pills}

### Baseline 1 Model 

```{r, include=TRUE}
reaction_time_mod_1_all <- lm(user_reaction_time_composite_score_1 ~ user_age_1 + org_name_1 + user_current_sport_1, data = baseline_final)

summary(reaction_time_mod_1_all)
```

### Baseline 2 Model 

```{r, include=TRUE}
reaction_time_mod_2_all <- lm(user_reaction_time_composite_score_2 ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(reaction_time_mod_2_all)
```

### Score Increase Model 

```{r, include=TRUE}
reaction_time_diff_baseline_mod_all <- lm(reaction_time_diff ~ user_age_2 + org_name_2 + user_current_sport_2, data = baseline_final)

summary(reaction_time_diff_baseline_mod_all)
```